Statement of Intent

### 2010-12-15 applications/phd_programs/berkeley_personal_history.tex
Done with my phd application stuff

After my freshman year of college, I spent two years as a volunteer missionary
in Alabama, paying my way to serve the hispanic community in that state.  I
learned Spanish in order to communicate with them, and I came to understand
much better the circumstances that immigrants to our country live in.  I did a
significant amount of Spanish-English interpretation, and it was in that
capacity that I first thought about the potential for computer science to
improve the lives of ordinary people.  What if a computer could interpret live
speech from one language to another, accurately and effectively?  Such a system
would ease the burdens on so many immigrants who have great difficulty
communicating with other people for their daily needs, and not just those in
our country.

@@

I also had a great internship experience as an undergraduate that helped to
shape my vision of what I want from my career.  I worked as an intern on the TV
Ads team at Google during the summer of 2009.  My intern host didn't have a
clear idea for the project she wanted me to do, so I proposed a meaningful,
difficult project that, if it worked, would have a large impact on the
company's business.  My host supported me and gave me the help that I needed,
and the project turned out to be very successful.  The project was so
successful that the director of all of TV Ads at Google said that my project
was the most important work going on in the whole TV Ads team, and several
times he commended me for my work.  One of the main things I learned from the
experience was that while I enjoy writing software, I find much more
satisfication in solving interesting problems that actually improve people's
lives.  I was able to help the TV Ads team, which was struggling to make money,
greatly improve their business.

@@

My first semester as a masters student during the summer of 2010 gave me my
first real teaching opportunity.  While I have tutored other students
throughout all of my college career, I had never done so in a formal setting.
That semester, however, I was a teaching assistant for two classes that Dr.
Seppi taught: Introduction to Articial Intelligence, and Bayesian Inference.  I
had always enjoyed helping people understand concepts, but I didn't realize how
much I would like the teaching aspect of being a professor until that
experience.  I found that figuring out how to explain complicated concepts
simply and seeing the light of understanding in the students' faces gave me
great satisfaction.

>>>>

After my freshman year of college, I spent two years as a volunteer missionary
in Alabama, paying my way to serve the Hispanic community in that state.  I
learned Spanish in order to communicate with them, and I came to understand
much better the circumstances that immigrants to our country live in.  I did a
significant amount of Spanish-English interpretation, and it was in that
capacity that I first thought about the potential for computer science to
improve the lives of ordinary people.  What if a computer could interpret live
speech from one language to another, accurately and effectively?  Such a system
would ease the burdens on so many immigrants who have great difficulty
communicating with other people for their daily needs, and not just those in
our country.

@@

I also had a great internship experience as an undergraduate that helped to
shape my vision of what I want from my career.  I worked as an intern on the TV
Ads team at Google during the summer of 2009.  My intern host didn't have a
clear idea for the project she wanted me to do, so I proposed a meaningful,
difficult project that, if it worked, would have a large impact on the
company's business.  My host supported me and gave me the help that I needed,
and the project turned out to be very successful.  The project was so
successful that the director of all of TV Ads at Google said that my project
was the most important work going on in the whole TV Ads team, and several
times he commended me for my work.  One of the main things I learned from the
experience was that while I enjoy writing software, I find much more
satisfaction in solving interesting problems that actually improve people's
lives.  I was able to help the TV Ads team, which was struggling to make money,
greatly improve their business.

@@

My first semester as a masters student during the summer of 2010 gave me my
first real teaching opportunity.  While I have tutored other students
throughout all of my college career, I had never done so in a formal setting.
That semester, however, I was a teaching assistant for two classes that Dr.
Seppi taught: Introduction to Artificial Intelligence, and Bayesian Inference.
I had always enjoyed helping people understand concepts, but I didn't realize
how much I would like the teaching aspect of being a professor until that
experience.  I found that figuring out how to explain complicated concepts
simply and seeing the light of understanding in the students' faces gave me
great satisfaction.
